% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[letterpaper, Biolinum]{article}

\usepackage{hyperref}
\usepackage{geometry}
\usepackage{amsmath}
\usepackage{booktabs}

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage{libertine}
%\usepackage[T1]{fontenc}
%\usepackage[sc,osf]{mathpazo}

% Set your name here
\def\name{\textbf{Carlos Rojas Quiroz}}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
\def\footerlink{https://carlosrojasquiroz.netlify.app}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {economics, statistics, mathematics},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 8.5in},
  left=1.0in,
  top=1.25in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}

\begin{document}

% Place name at left
{\huge \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\hrule 
\vspace{0.10in}
\begin{minipage}{0.45\linewidth}
  \href{http://economics.uc3m.es}{Carlos III University of Madrid (UC3M)} \\
  \href{http://economics.uc3m.es}{Department of Economics} \\
  Calle Madrid 126, 28903 \\
  Getafe, Spain.
\end{minipage}
\begin{minipage}{0.45\linewidth}
  \begin{tabular}{ll}
%    Phone: & (919) 962-1234 \\
%    Fax: &  (919) 962-5678 \\
    Email: & \href{mailto:carojasq@eco.uc3m.es}{carojasq@eco.uc3m.es} \\
    Homepage: & \href{https://carlosrojasquiroz.netlify.app}{https://carlosrojasquiroz.netlify.app} \\
  \end{tabular}
\end{minipage}
\vspace{0.1in}
\hrule

\section*{Education}
\vspace{-0.1in}
\hrule
\vspace{0.1in}
\begin{itemize} 
  \item \textit{Graduate Program in Economics}, Carlos III University of Madrid (2019-...).
  \item \textit{MSc in Economics}, Pontifical Catholic University of Chile (2015).
  \item \textit{BSc in Economics}, National Agrarian University La Molina (2011).
\end{itemize}


\section*{Teaching experience}
\vspace{-0.1in}
\hrule
\vspace{0.1in}
\begin{itemize} 
\item \textit{Part-time Lecturer} in Economic Growth, Monetary Theory and Applied Macroeconomics, Peruvian University of Applied Sciences (2017-2019).
\item \textit{Part-time Lecturer} in Macroeconomic Theory II and Dynamic Macroeconomics, National University of Engineering (2016-2018).
\item \textit{Teaching Assistant} in Dynamic Macroeconomics, National Agrarian University La Molina (2010).
\end{itemize}

\section*{Awards and Scholarships}
\vspace{-0.1in}
\hrule
\vspace{0.1in}
\begin{itemize} 
\item \textit{Winner of the Network Project on Fiscal Rules and the Behaviour of Public Investment}, Inter-American Development Bank (2019).
\item \textit{Graduate Scholarship}, Carlos III University of Madrid (2019). 
\item \textit{Academic Excellence Prize}, Pontifical Catholic University of Chile, (2015).
\item \textit{``Presidente de la Republica'' Scholarship}, Peruvian Government (2014-2015). 
\item \textit{Graduated with Honours}, National Agrarian University La Molina (2011). 
\item \textit{University Extension Course in Economics,} Central Bank of Peru (2010)
\end{itemize}

\section*{Professional experience}
\vspace{-0.1in}
\hrule
\vspace{0.1in}
\begin{itemize}
\item \textit{Senior Economist}, Technical Secretariat at the Fiscal Council of Peru (2018-2019).
\item \textit{Economist}, National Council of Science, Technology and Technological Innovation (2016-2018).
\item \textit{Economist/Consultant}, Ministry of Economy and Finance (2011-2014 and 2016).

\end{itemize}


\section*{Publications}
\vspace{-0.1in}
\hrule
\vspace{0.1in}
\subsection*{Journal Articles}

\begin{itemize}
\item Optimal Monetary Policy under Financial Instability in Emerging Market Economies, 2018, {\it Econom\'ia Chilena}, Vol. 21 No. 1 pp. 68--117.
\item Optimal Monetary and Macroprudential Policies after Basel III, 2017, {\it Estudios Econ\'omicos}, No. 33, pp. 57--94.
\end{itemize}

\subsection*{Policy Papers}

\begin{itemize}
\item Fiscal Risks: Analysis of the Macrofiscal Projections from the Multiannual Macroeconomic Framework, 2019, {\it Discussion Notes of the Technical Secretariat at the Fiscal Council of Peru}, No. 001-2019-CF/ST. With Gustavo Ganiko.
\item Fiscal Stance and the Business Cycle, 2018, {\it Discussion Notes of the Technical Secretariat at the Fiscal Council of Peru}, No. 001-2018-CF/ST. With Renatto Vassallo.
\item Peruvian Fiscal Policy: Methodological Adjustments of the Structural Balance Calculation, 2016, {\it Moneda}, No. 167, pp. 32-.36. With Nikita C\'espedes, Patricia Lengua and Jes\'us Rodr\'iguez. 
\item The Structural Balance, an Analytical Tool for the Fiscal Policy, 2012, {\it Research Papers of the Ministry of Economy and Finance of Peru}. With Alejandro Granda and C\'esar Liendo.
\end{itemize}

\section*{Skills}
\vspace{-0.1in}
\hrule
\vspace{0.1in}
\subsection*{Software}
Matlab, Python, Stata, Eviews, R, \LaTeX\
\subsection*{Languages}
Spanish (native) and English (fluent).

\bigskip

% Footer
\begin{center}
  \begin{footnotesize}
    Last updated: \today \\
    \href{\footerlink}{\texttt{\footerlink}}
  \end{footnotesize}
\end{center}

\end{document}